Community context determines competition vs. facilitation trade-offs in pollination systems

### 2019-05-07 paper/manuscript.Rmd
Update title and running title

<!-- ^a^ [efc29@uclive.ac.nz](mailto:efc29@uclive.ac.nz); ^b^ [hugomarrero@gmail.com](hugomarrero@gmail.com); ^c^ [jason.tylianakis@canterbury.ac.nz](jason.tylianakis@canterbury.ac.nz); ^d^ [daniel.stouffer@canterbury.ac.nz](daniel.stouffer@canterbury.ac.nz) -->

@@

**Data accessibility:** Data supporting the results will be accessible in an appropriate data repository after publication. The data DOI will be included here.

>>>>

**Running title:** 
Competition for pollination vs. facilitation

@@

**Data accessibility:** Data supporting the results will be accessible in an appropriate data repository after publication. The DOI will be included here.
